Understanding the Lomb-Scargle Periodogram

### 2016-12-20 PracticalLombScargle.tex
More material for pseudo-nyquist section

\subsection{A Non-uniform Nyquist Limit?}

@@

@@

\citet{Horne86}:
\begin{quote}
The largest frequency we calculated was $\pi N-)/T$ which
is the traditional Nyquist frequency for evenly-spaced data. The Nyquist
frequency is not well defined for unevenly spaced signals, but it can serve as
a reasonable upper limit for the calculation.
\end{quote}

@@

>>>>

\subsection{A Non-uniform Nyquist Limit?}
\sectlabel{pseudo-nyquist}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{fig12_pseudo_nyquist}
  \caption{An example of data for which the various poorly-motivated
    ``pseudo-Nyquist'' approaches outlined in \sect{pseudo-nyquist} fail
    spectacularly. The upper panels show the data, a noisy sinusoid with
    a frequency of 100 (i.e. a period of 0.01).
    The lower left panel shows a histogram of spacings between observations:
    the minimum spacing is 2.5, meaning that the signal has
    {\it over 250 full cycles} between the minimum spacing.
    Nevertheless, the periodogram (lower right) clearly identifies the correct
    period, though it's orders of magnitude larger than Nyquist estimates based
    on average or minimum sampling rate.
    \figlabel{pseudo_nyquist}}
\end{figure}

@@

@@

\appendix

\section{Non-uniform Nyquist}
A selection of quotations showing approaches to a non-uniform Nyquist limit:

\begin{description}

\item[Average Sampling Rate]

\citet{Horne86}:
\begin{quote}
The largest frequency we calculated was $\pi N/T$ which
is the traditional Nyquist frequency for evenly-spaced data. The Nyquist
frequency is not well defined for unevenly spaced signals, but it can serve as
a reasonable upper limit for the calculation.
\end{quote}

\item[Harmonic Average of Sampling Rate]

\item[Minimum Sample Spacing]

\item[Getting it Right]

\citet{Eyer99}

\end{description}
